---
title       : Death Prediction Evaluation Service
subtitle    : or Helping People Cope with the Inevitable
author      : Wayne Witzke
framework   : io2012
highlighter : highlight.js
hitheme     : tomorrow
widgets     : [mathjax]
mode        : selfcontained
---

```{r setup, echo=FALSE, results="hide", cache=FALSE}
library(ggplot2);
```

##  The Problem

```{r SURPRISE, fig.width = 13, fig.height = 6, echo=FALSE, cache=FALSE}
s.data = data.frame(
    age = seq(0,120,0.1),
    surprise = exp(4.7*( pi/2 - atan( ( seq( 0, 120, 0.1 ) - 70 )/8 ) )) +
               ifelse(seq(0, 120, 0.1)-79<0,0,1)*(seq( 0, 120, 0.1) - 79)^38 / (exp( 12+1.8*seq( 0, 120, 0.1) - 79 ))
);
s.plot = ggplot( s.data, aes( age, surprise ) ) +
         geom_line( aes( age, surprise ), s.data ) +
         scale_y_log10( name = "Zalikey's Asjusted Expectation Response (log scale)", breaks = c(0, 10, 100, 1000, 10000, 100000,1000000)) +
         xlab("Age") +
         ggtitle("Expectation Response due to Death as Measured at Various Ages");

s.plot
```

* People under the age of 50 are nearly 1 million times more surprised by their
  own demise (than people over the age of 110)!

---

##  Bad for Society

```{r negative_outcomes, echo = FALSE, fig.width = 13, fig.height = 6, cache=FALSE}
no.data = data.frame(
    outcome = c("Anxiety", "Hair Loss", "Confusion", "Accidental Dismemberment", "Hunger", "Public Humiliation", "Death"),
    count = c( 15, 4, 43, 9, 13, 21, 892 )
);
no.data$outcome = factor(no.data$outcome, levels = no.data$outcome);

no.plot = ggplot( no.data, aes( x = outcome, y = count, fill = outcome ) ) +
          geom_bar( stat = "identity", show.legend = FALSE ) +
#          theme(
#            axis.text.x = element_text( angle = -60, hjust = 0 )
#          ) +
          ggtitle( "MITT Survey of Negative Outcomes Associated with Surprise Arising from Death") +
          xlab( "Negative Outcome Type" ) +
          ylab( "Number of Occurances (out of 1000)") +
          scale_fill_discrete( name = "" );

no.plot
```

* Clearly, reducing surprise of death is important for the health and well-being of society!

---

## Our Proposal:<br>The Death Prediction Evaluation Service

* Software that evaluates personal estimates for remaining years before death
* Provides feedback regarding the quality of those estimates, and helpful tips
  if those estimates were somewhat off
* Collects and displays data regarding the estimates made by others
  * Provides comfort by showing people they are not alone!
  * Gives people a quantitative measure for how much they need to manage their
    expectations!
* After deployment, we predict an eventual 95% reduction in the adjusted
  expectation response in people under 50 years of age
  * Young people will then be more like people over the age of 110!
* https://wwitzke.shinyapps.io/dpredevalserv/

---

## Preliminary Study Results

```{r SURPRISE_revisited, fig.width = 13, fig.height = 5, echo=FALSE, cache=FALSE}
#set.seed(as.numeric(Sys.time()));
set.seed(100);
ages = runif( 30, 5, 120 );
sim.noise = rnorm( 30, 0, 500 );
sn.data = data.frame(
    age = ages,
    surprise = abs((1+sim.noise)*exp(4.7*( pi/2 - atan( ( ages - 20 )/8 ))) +
               ifelse(ages-79<0,0,1)*(ages - 79)^38 / (exp( 12+1.8*ages - 79 ))
));
sn.plot = ggplot( sn.data, aes( age, surprise ) ) +
         geom_point( aes( age, surprise ), sn.data ) +
         scale_y_log10( name = "Zalikey's Asjusted Expectation Response (log scale)", breaks = c(0.01,0.1, 1, 10, 100, 1000, 10000, 100000,1000000)) +
         xlab("Age") +
         ggtitle("Expectation Response due to Death in 30 Survey Respondants of Various Ages After Using Software") +
         geom_smooth();

sn.plot
```

* Clearly significant reduction in response in respondants under 50 years of age!
* Note impressively small confidence interval of fit line!
* Please give us money!

